### 2016-08-26 notions.tex
comments

\jnote{OK, from here on I specialize to set-representation data structures\ldots}
The one-wayness definition (see
Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
sets. \jnote{I got rid of the weaker definition, since it seems unnatural to me.}
A set $S$ is chosen from this distribution, and a representation
$(M,\pubaux,\privaux)$ of that set is computed.
In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
In both cases, the attacker is given
access to an oracle via which it can
issue queries and obtain the corresponding responses.
For a given $\distr{}{}$ and $A$, we define the advantage measure
$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{A}=1} \right|$.
We track the
time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.

@@

\jnote{I'm not sure whether we want to limit consideration to ``high-entropy''
distributions
and require the probability of finding an element to be low,
or whether we want to allow arbitrary distributions but compare the attacker's
success probability when given $(M, \pub)$ to its success probability when given nothing.
The latter seems cleaner, so I took that approach here.}

\jnote{Actually, I am unsure whether a one-wayness definition is independently
interesting if we have (and can achieve) a semantic-security definition.}

Our semantic-secure definition is simulation-based (see
Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
$M,\pubaux$ that result from running $\Rep(S)$.
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{Note
there is no need for a query oracle here, since the attacker knows the set. Interestingly,
if we provide a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then this definition seems to imply
correctness also.}
\tsnote{Need to pass state between stages if you want~$A$ to know the
  set it previously sampled, right?}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\calS} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \calS}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage ${\sf leak}$
if there is a simulator $\calS$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\calS}$ is small
for all~$A$. Intuitively, this means that the public portion
$M, \pubaux$ of the representation of a set~$S$ leaks only ${\sf leak}(S)$.

>>>>

\jnote{OK, from here on I specialize to set-representation data structures\ldots}
The one-wayness definition (see
Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
sets. \jnote{I got rid of the weaker definition, since it seems
  unnatural to me.}\tsnote{Why? It captures things like the Squid
  summary cache -- hash functions are public (in the code, in the
  literature), but you would need to corrupt the HTTP proxy-server to
  get the representation.}
A set $S$ is chosen from this distribution, and a representation
$(M,\pubaux,\privaux)$ of that set is computed.
In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
In both cases, the attacker is given
access to an oracle via which it can
issue queries and obtain the corresponding responses.
For a given $\distr{}{}$ and $A$, we define the advantage measure
$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{A}=1} \right|$.
We track the
time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.

@@

\jnote{I'm not sure whether we want to limit consideration to ``high-entropy''
distributions
and require the probability of finding an element to be low,
or whether we want to allow arbitrary distributions but compare the attacker's
success probability when given $(M, \pub)$ to its success probability when given nothing.
The latter seems cleaner, so I took that approach here.}\tsnote{I
guess I prefer the former.  Security bounds will always surface the (elementwise)
min-entropy of~$\distr{}{}$.  In any case, it's not clear to me that
the null experiment captures reference/trivial attacks, which is what
I think you are trying to capture with it.  I mean, why not give the
public information? }

\jnote{Actually, I am unsure whether a one-wayness definition is independently
interesting if we have (and can achieve) a semantic-security definition.}
\tsnote{Depends on what information we decide is okay to leak.  A
  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
Do we want that to be considered semantically secure?  On the other
hand, a classical BF is one-way in the ROM, up to the min-entropy of
the distribution over~$S$.  So that may already give an interesting
example that fits in the gap.}
Our semantic-secure definition is simulation-based (see
Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
$M,\pubaux$ that result from running $\Rep(S)$.
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{Note
there is no need for a query oracle here, since the attacker knows the set. Interestingly,
if we provide a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then this definition seems to imply
correctness also.}
\tsnote{Need to pass state between stages if you want~$A$ to know the
  set it previously sampled, right?}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\calS} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \calS}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage ${\sf leak}$
if there is a simulator $\calS$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\calS}$ is small
for all~$A$. Intuitively, this means that the public portion
$M, \pubaux$ of the representation of a set~$S$ leaks only ${\sf leak}(S)$.
